Cover letter for the IJRR submission \\ ``An efficient acyclic contact planner for multiped robots''

### 2017-01-20 body/contact.tex
Review 5.1 and 6.4

>>>>

\subsection{Definition of a contact sequence}
In previous contributions\adnote{Add reference here}, a contact plan is defined as a sequence of \deladp{configurations that describe a} quasi-static equilibrium configurations
for each \repadp{contact}{existing} phase \deladp{of the motion}. For instance, a walk cycle would be described by three key configurations: a double-support configuration, a single-support configuration (a contact is broken), and another double-support configuration (a contact is created). 
Our definition of contact plan differs: between two consecutive configurations we allow both a contact break and a contact creation---if they are on the same effector. 
In the previous example, our contact plan would simply consist of the two double-support configurations. 
%However, if the contact broken and the contact created sequentially are not on the same effector, our planner outputs two distinct states.
This representation is sufficient to describe all the contact constraints of the problem. Furthermore it removes the need to have single-support quasi-static configurations as in the example. 
As shown in the companion video, this allows our framework to produce dynamic motions.

### 2017-01-20 body/results.tex
Review 5.1 and 6.4

\subsection{Validation of the contact plans, and comparison with previous work} \label{sec:compa}
To validate our plans, we either use the framework proposed by \citeauthor{Carpentier2016} or our own implementation of a $\mathcal{P}_3$ solver, detailed in Appendix~\ref{app:optim}.
The obtained motions are available in the video.

Few contributions provided computation times on the complete problem, necessary to provide comparison between our approaches. 
Furthermore, $\mathcal{P}_3$ remains an open problem in the presence of obstacles. The only valid scenarios addressed completely in previous works are thus the stair climbing scenarios of different heights proposed by \citeauthor{Hauser06usingmotion}, and the table egress scenario by ~\citeauthor{DBLP:conf/iser/EscandeKMG08}, which we consider to be of similar complexity with respect to the car egress scenario (we did not consider the stairs in the scene). Both scenarios use HRP-2.

Table~\ref{tab:compprev} presents the computation times we obtained for these scenarios, clearly demonstrating that our approach is order of magnitude faster that previous works.

>>>>

\subsection{Validation of the contact plans, and comparison with previous work} \label{sec:compa}
To validate our plans, we either use the framework proposed by \citeauthor{Carpentier2016} or our own implementation of a $\mathcal{P}_3$ solver, detailed in Appendix~\ref{app:optim}.
The companion video shows the obtained motions.

Few contributions provided computation times on the complete problem. %, necessary to provide comparison between our approaches. 
Furthermore, $\mathcal{P}_3$ remains an open problem in the presence of obstacles. The only valid scenarios addressed completely in previous works are thus the stair-climbing scenarios of different heights proposed by \citeauthor{Hauser06usingmotion}, and the table-egress scenario by~\citeauthor{DBLP:conf/iser/EscandeKMG08}, which we consider to be of similar complexity with respect to the car-egress scenario (we did not consider the stairs in the scene). Both scenarios are tested with HRP-2.

Table~\ref{tab:compprev} presents the computation times for these scenarios, clearly demonstrating that our approach is order of magnitude faster than previous works.
